Temporality is Important for Networks of Hospital Patient Transfers

### 2025-05-06 reports/report.qmd

Beyond simple models, there is vanishingly small possibility of finding tractable analystical expressions for the hitting times.

## Experimental Setup

We initialise the state of a simulation by seeding 30 individuals in a single facility.
We then simulate the system forwards in time until a fixed end time.

Each starting facility is looped over to be the starting facility, and realisations are acquired 20 times for each starting facility.
This gives pairs of hitting times between the (known) starting facility and target facility (which we get for all non-starting facilities by the end of the simulation realisation)

>>>>

Beyond simple models, there is vanishingly small possibility of finding computable analytical expressions for the hitting times.
Instead we examine the empirical distributions from simulating the dynamics.
To do this, we iterate over all facilities, seeding 30 individuals in that single facility, and simulating until a fixed end time, using a discrete-time Markov Chain formulation.
We note the number of individuals in each facility at each time step.
The central metric we will examine is the hitting time.
In these experiments, to e

## Results

```{python}

```

Plotting the aggregated hitting times as an empirical cumulative distribution function (ECDF) in @fig-ecdf, we can see that
